%-------------------------------------------
% Curriculum Vitae (CV) in LaTeX
% Author : Mehdi Karami
% License : MIT
%-------------------------------------------

%------Required Packages and Functions------
\documentclass[letter,10pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[dvipsnames]{xcolor}
\usepackage{fontawesome5}
\usepackage{hyperref}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage{tabularx}
\usepackage{lmodern}
\usepackage{microtype}

% Document setup
\geometry{left=0.5in, right=0.5in, top=0.5in, bottom=0.5in} % Set page margins
% \raisebox{4mm}{\hbox to 0pt{\small Last Update: \textbf{September, 2025}\hss}\hbox to\textwidth{\hfill\thepage\hfill}}
\makeatletter
\def\ps@plain{
  \def\@oddhead{\headername}
  \let\@evenhead\@oddhead
  \def\@oddfoot{
    \raisebox{4mm}{\hbox to 0pt{}\hbox to\textwidth{\hfill\thepage\hfill}}
  }
  \let\@evenfoot\@oddfoot
}
\makeatother
\pagestyle{plain}

% Section and subsection formatting
\definecolor{tintColor}{RGB}{70,91,136} % Define theme color
\titleformat{\section}{\color{tintColor}\large\bfseries}{}{0em}{}[\titlerule] % Format section titles
\titleformat{\subsection}{\bfseries}{}{0em}{}[\vspace{-0.5em}] % Format subsection titles

\setlength{\tabcolsep}{18pt} % Adjusting space around the table
\setlist[itemize]{topsep=5pt, itemsep=0.5em, parsep=0pt, partopsep=0pt}

% Hyperlink setup
\hypersetup{
    urlbordercolor = black, % Border color for URLs
    pdfborderstyle = {/S/U/W 0} % Border style for PDF links
}

%--------------Custom Commands--------------
\newcommand{\customsquare}{\raisebox{0.25ex}{\scalebox{0.45}{$\blacksquare$}}}
\newcommand{\headername}{
  \ifnum\value{page}>1
    \raisebox{-4mm}{\textbf{Mehdi Karami}}
  \fi
}

% Personal information
\newcommand{\name}{\textcolor{tintColor}{Mehdi} Karami} % Name
\newcommand{\phone}{+98 (990) 956-2438} % Phone Number
\newcommand{\email}{karami.mehdi.scholar@gmail.com} % Email

%%%%%%%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%
\begin{document}

%-----------------HEADING-------------------
\begin{center}
\renewcommand{\arraystretch}{1.5}
\begin{tabular}{@{} p{\linewidth} @{}}
\textbf{\huge \name} \hfill \href{mailto:\email}{\underline{\small \faEnvelope\ \email}} \hfill \href{tel:\phone}{\underline{\small \faPhone\ \phone}} \hspace{14mm} \hfill\\
{\small \faLocationArrow\ Shiraz, Iran} \hfill \hfill \href{https://github.com/karami-mehdi}{\underline{\small \faGithub\ github.com/karami-mehdi}} \hspace{2mm} \hfill \href{https://www.linkedin.com/in/karami-mehdi}{\underline{\small \faLinkedin\ linkedin.com/in/karami-mehdi}}\\ % LinkedIn profile
\end{tabular}
\end{center}

%-----------------SUMMARY-------------------
\section*{Summary}
\begin{itemize}[label={\customsquare}]
    \item Machine Learning Researcher with expertise in developing AI models, having established a pre-trained GAN for limited-labeled brain MRI segmentation, producing advances in automated neuroimaging and contributing to scientific and clinical research.
    \item Skilled Programmer proficient in multiple programming languages and technologies, with practical experience as an iOS Developer for an international company, having led workshops and won first place in a coding competition, which demonstrate strong technical expertise, teamwork, and effective communication in collaborative settings.
    \item Active Open-Source Contributor, collaborating on public and volunteer projects, fostering knowledge sharing and providing tools for developer and research communities.
\end{itemize}

%-----------------EDUCATION-----------------
\section*{Education}
\textbf{Bachelor of Computer Engineering} -  GPA: 3.57/4.00 (equivalent to 17.88/20) \hfill Sep 2021 - Aug 2025 \\
Zand Institute of Higher Education  \hfill Shiraz, Iran \\[5pt]
\mbox{Visiting Student\hspace{0.1mm}\llap{Visiting Student}} \hfill Feb 2023 - Jul 2024 \\
University of Science and Culture \hfill Tehran, Iran

%------------RESEARCH INTERESTS-------------
\section*{Research Interests}
\setlength{\tabcolsep}{18pt} % Adjusting space around the table

\begin{tabularx}{\textwidth} { 
    >{\customsquare \hspace{1mm} \raggedright\arraybackslash}X 
    @{\extracolsep{\fill}}
    >{\customsquare \hspace{1mm} \raggedright\arraybackslash}X
    @{\extracolsep{\fill}}
    >{\customsquare \hspace{1mm} \raggedright\arraybackslash}X
    @{\extracolsep{\fill}}
    }
Machine learning & Deep Learning & Computer Vision \\
Computational Biology & Scientific Computing & Algorithm Design
\end{tabularx}

%-------------PUBLICATION---------------
\section*{Publication}
\textbf{Pre-Trained Generative Adversarial Network for Limited-Labeled Brain MRI Segmentation} \\ [5pt]
Authors: Mehdi Karami*, Dr. Betsabeh Tanoori \hfill *Primary author, Manuscript in preparation \\
Code: To be released as open-source

%-------------TEACHING EXPERIENCE---------------
\section*{Teaching Experience}
\textbf{Teaching Assistant (TA)} \hfill Zand Institute of Higher Education, Shiraz, Iran \\ [5pt]
\begin{tabularx}{\textwidth}{@{}X X@{}}
    \customsquare\hspace{2mm}\textbf{Fall 2024:} 
    \begin{itemize}
        \item Human-Computer Interaction
        \item Digital Electronics
    \end{itemize}
    &
    \customsquare\hspace{2mm}\textbf{Spring 2025:} 
    \begin{itemize}
        \item Fundamentals of Computer and Programming
        \item Digital Electronics
        \item Computer Architecture
    \end{itemize}
\end{tabularx} \\ [-20pt]

%-------------WORK EXPERIENCE---------------
\section*{Work Experience}
\textbf{iOS Developer} \hfill Jun 2023 -- Jun 2024 \\ [3pt]
\href{https://roundtableapps.com}{\underline{Round Table Apps}} \hfill Development Office, Tehran, Iran \\ [8pt]
Contributed to the development of diverse, international-scale applications across various domains, including healthcare, finance, and postal transportation.

\begin{itemize}[label={\customsquare}]    
    \item \href{https://app.resiliencebox.com}{\underline{\textbf{Resilience Box}}}
    \begin{itemize}
        \item Healthcare app focused on mental health management, providing online learning resources, well-being videos, an in-depth podcast series, informational fact sheets, and access to counseling and coaching services.
    \end{itemize}

    \item \href{https://www.blossomapp.com}{\underline{\textbf{Blossom -- Save and Invest}}}
    \begin{itemize}
        \item Savings app that helped users in Australia and New Zealand reach their financial goals faster by providing access to high-interest savings products.
    \end{itemize}
    
    \item \href{https://mailplus.com.au}{\underline{\textbf{MailPlus}}}
    \begin{itemize}
        \item Postal transportation app designed for postal service drivers across Australia.
    \end{itemize}
\end{itemize}

\textbf{Technical Contributions:}
\begin{itemize}[label={\customsquare}]
    \item Utilized architectural and design patterns, such as Repository, VIP, MVC, and Clean Architectures, to manage project structure and layers.
    \item Conducting detailed research on the optimal utilization and development of augmented reality (AR) and virtual reality (VR) technologies, utilizing visionOS and other relevant technologies.
    \item Performed comprehensive research and analysis of data flow to ascertain the behavioral patterns of applications across various scenarios.
    \item Applied optimization techniques for real-time data processing.
    \item Implemented algorithms for financial calculations and optimizations.
    \item Conducted Behavior-Driven Development (BDD) to ensure robust and high-quality code.
    \item Created detailed documentation with Xcode DocC and Confluence.
    \item Collaborated with iOS and other teams including BackEnd, Test, Design, FrontEnd, and Android teams, using Scrum, Jira, and other management tools.
\end{itemize}

%-----------OPEN SOURCE PROJECTS------------
\section*{Open Source Projects}
\begin{itemize}[label={\customsquare}]
    \item \href{https://github.com/karami-mehdi/CyberattackDetection}{\underline{\textbf{Cyberattack Detection and Anomalous Behavior Analysis}}}
    \begin{itemize}
        \item Utilizes a Recurrent Neural Network (RNN), technically Long Short-Term Memory (LSTM), to detect cyberattacks based on anomalous behavior in network traffic. The model identifies abnormal patterns associated with attacks, e.g., DDoS, port scanning, and brute-force attempts.
        \item Stack: Python, Keras (TensorFlow), Scikit-learn, Principal component analysis (PCA), Receiver Operating Characteristic (ROC) Curve, …
    \end{itemize}

    \item \href{https://github.com/karami-mehdi/SolarPowerGenerationAnalysis}{\underline{\textbf{Solar Power Generation Prediction}}}
    \begin{itemize}
        \item Implements multiple machine learning models, i.e., Linear Regression, Decision Tree Regressor, Gradient Boosting Regressor, Random Forest Regressor, Multi-layer Perceptron (MLP) Regressor, and Deep Neural Network (DNN), to predict solar power generation. Models are evaluated using performance metrics such as Mean Absolute Error (MAE), Mean Squared Error (MSE), Coefficient of Determination ($R^2$), and Confusion Matrix to ensure accurate predictions.
        \item Stack: Python, Scikit-learn, TensorFlow, Pandas, Matplotlib, NumPy, Seaborn, ...
    \end{itemize}

    \item \href{https://github.com/karami-mehdi/AISightQuest}{\underline{\textbf{AI Sight Quest}}}
    \begin{itemize}
        \item Utilizes AI to extract text from images via Apple's Vision Framework and provides instant answers to document questions using the Bidirectional Encoder Representations from Transformers (BERT) language model.
        \item Stack: Machine Learning, Deep Learning, Swift, SwiftUI, SwiftData, Model-view-viewmodel (MVVM), Vision Framework, Speech Framework, TipKit, …
    \end{itemize}

    \item \href{https://github.com/karami-mehdi/ProximityFinder}{\underline{\textbf{Proximity Finder}}}
    \begin{itemize}
        \item Efficiently detects the nearest point pair on a 2D screen with O(n log n) complexity using Divide and Conquer. Includes an interactive slider for dynamic point adjustment.
        \item Stack: Swift, UIKit, Model-View-Controller (MVC), Algorithm Design, Algorithm Optimization, Core Graphics, … 
    \end{itemize}

    % \item \href{https://github.com/karami-mehdi/BookBench}{\underline{\textbf{Book Bench}}}
    % \begin{itemize}
    %     \item Streamlines library seat reservations. Key features include sign-up, login, and password reset functionality using Firebase authentication and database.
    %     \item Stack: Swift, SwiftUI, MVVM, Reactive Programming, Lottie JSON, Figma, …
    % \end{itemize}

    \item \href{https://github.com/karami-mehdi/Heart-Pulse-Detector-Using-Arduino}{\underline{\textbf{Heart Pulse Detector - Beats Per Minute (BPM) Counter}}}
    \begin{itemize}
        \item Programs a BPM calculator using an Arduino Uno to monitor heart rate and display pulse data through a real-time heart rate graph.
        \item Stack: Arduino C/C++, Data Processing, Sensor Integration, Display Handling, ...
    \end{itemize}

    \item \href{https://github.com/karami-mehdi/CommandLineGame}{\underline{\textbf{Command-line Game}}}
    \begin{itemize}
        \item Designs and implements interactive command-line games, emphasizing scalable architecture, efficient logic processing, and a seamless user experience.
        \item Stack: Swift, Protocol-Oriented Programming (POP), Clean Architecture, …
    \end{itemize}
\end{itemize}

\small \textbf{Additional projects can be found at: \href{https://github.com/karami-mehdi}{\underline{GitHub account}}.}

%---------------VOLUNTEERING----------------
\section*{Volunteering}
\textbf{Workshop on Git and GitHub} \hfill Dec 2024 \\ [2pt]
Zand Institute of Higher Education \hfill Shiraz, Iran \\ [5pt]
\href{https://github.com/karami-mehdi/CV/blob/main/Assets/certificate-of-workshop-participation-karami-mehdi.pdf}{\underline{\textbf{Workshop on Git and GitHub (Techniques for Effective Collaboration)}}} \hfill May 2024 \\ [2pt]
Credential ID 400434784 \hfill Tehran, Iran \\ 
K. N. Toosi University of Technology \\ [5pt]
\textbf{Contributor of \href{https://github.com/swiftlang/swift-evolution}{\underline{\textbf{Swift Evolution GitHub Repository}}}} \hfill Since Dec 2023 \\ [2pt]
Participated in the proposals of the Swift Evolution repository.

%--------------HONORS & AWARDS--------------
\section*{Honors \& Awards}
\noindent
\textbf{Winning First Place in the C++ Programming Language Competition} \hfill May 2022 \\
Hosted by Zand Institute of Higher Education \hfill Shiraz, Iran

%---------------CERTIFICATES----------------
\section*{Certificates}
\noindent
\href{https://www.mindluster.com/storage/cer/1688271634.jpg}{\underline{\textbf{Swift for Beginners}}} \hfill Issued by Mind Luster \\ [2pt]
Credential ID 1688271634 \hfill Mar 2023 \\ [5pt]
\href{https://www.sololearn.com/certificate/CT-QD4IETGO/png}{\underline{\textbf{Theoretical understanding of Swift 4}}} \hfill Issued by Sololearn \\ [2pt]
Credential ID CT-QD4IETGO \hfill Jan 2023

%-------------LANGUAGE---------------
\section*{Language}
\noindent
\textbf{English:} Fluent \hspace{2em} 
\textbf{Persian–Turkish:} Native

%-------------TOEFL---------------
\section*{TOEFL}
\textbf{Total Score: 89}
\hspace{4em}
\begin{tabularx}{0.7\textwidth} { 
    >{\customsquare\hspace{2mm}\raggedright\arraybackslash}X 
    @{\extracolsep{\fill}}
    >{\customsquare\hspace{2mm}\raggedright\arraybackslash}X
    @{\extracolsep{\fill}}
    >{\customsquare\hspace{2mm}\raggedright\arraybackslash}X
    @{\extracolsep{\fill}}
    >{\customsquare\hspace{2mm}\raggedright\arraybackslash}X
    @{\extracolsep{\fill}}
    }
Reading: \textbf{23} & Listening: \textbf{22} & Speaking: \textbf{19} & Writing: \textbf{25}
\end{tabularx}

%------------------EXTRACURRICULAR ACTIVITIES------------------
\section*{Extracurricular Activities}

\begin{tabularx}{\textwidth} { 
    >{\customsquare\hspace{2mm}\hsize=0.5\hsize\centering\arraybackslash}X
    >{\customsquare\hspace{2mm}\hsize=0.5\hsize\centering\arraybackslash}X
    >{\customsquare\hspace{2mm}\hsize=1\hsize\centering\arraybackslash}X
    >{\customsquare\hspace{2mm}\hsize=0.8\hsize\centering\arraybackslash}X
}
Swimming & Traveling & Cooking International Cuisine & Esports Gaming (LOL)
\end{tabularx}

%------------------REFERENCES------------------
\section*{References}
\noindent
\vtop{\hbox{\customsquare\hspace{2mm}\textbf{Dr. Betsabeh Tanoori}}
\hbox{\quad Associate Professor}
\hbox{\quad Department of Computer Engineering}
\hbox{\quad Zand Institute of Higher Education}
\hbox{\quad Shiraz, Iran}
\hbox{\quad \texttt{b.tanoori@zand.ac.ir}}}%
\hfill
\vtop{\hbox{\customsquare\hspace{2mm}\textbf{Dr. Azadeh Tabatabaei}}
\hbox{\quad Associate Professor}
\hbox{\quad Department of Computer Engineering}
\hbox{\quad University of Science and Culture}
\hbox{\quad Tehran, Iran}
\hbox{\quad \texttt{a.tabatabaei@usc.ac.ir}}}%
\hfill
\vtop{\hbox{\customsquare\hspace{2mm}\textbf{Dr. Amir Hossein Rasekh}}
\hbox{\quad Associate Professor}
\hbox{\quad Department of Computer Engineering}
\hbox{\quad Zand Institute of Higher Education}
\hbox{\quad Shiraz, Iran}
\hbox{\quad \texttt{ahrasekh@zand.ac.ir}}}

\end{document}